Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-10-17 analysis/output/figures/hypotheses/Hypotheses.Rmd
Adding more granular plots

```{r plot-marginals, echo = FALSE}
# Specify the covariate.
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 1                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

    "Importance of trusing charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",

@@

if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
    draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    filter(
    # levels ==   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
      covariates ==  "Income: Less than $10,000 to $300,000 or more") %>% 
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

>>>>

```{r plot-marginals, echo = FALSE}
# Specify the covariate.
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 1                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

    "Importance of trusting charities: Not at all to Essential", "Trust in charities: None to Complete", "Donation frequency: Weekly to Never",

@@

if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
    draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    filter(
      # levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
      covariates == str_c(
      c("Church or religious organization: ", "Sport or recreational organization: ", "Art, music, or educational organization: ",
        "Labor union: ", "Political party: ", "Environmental organization: ", "Professional association: ", 
        "Humanitarian or charitable organization: ", "Consumer organization: ", "Other organization: "
      ), 
      "Member to Not")) %>% 
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 4)
}
```

### 2019-10-17 manuscript/manuscript.Rmd
Adding more granular plots

Compared to when an NGO has a friendly relationship with the host government, donors are much less likely to donate when government is under crackdown or criticized.

@@

@@

@@

    - Marital Status
  ![](output/figures/marital-status.png)  
  Question: it seems that levels like emergency response are omitted because they're considered the base to compare to. Why is there not a "Marital status: Married" though? It can't be the same thing

>>>>

Compared to when an NGO has a friendly relationship with the host government, donors who see that an NGO faces general legal trouble abroad are less likely to donate.

@@

    - Traveled Internationally: No
    ![](output/figures/traveled.png)

    - Medium to follow news: Online (excluding social media) with all attributes
      ![](output/figures/following-news.png)

    - Medium to follow news: Online (excluding social media) with organization
      ![](output/figures/following-news2.png)

@@

    - Can't get a plot of Religiosity to work.

@@

    - Marital Status
  ![](output/figures/marital-status.png)
